---
title: "Figure 4"
author: "Carolina Lobato"
date: "2024-08-10"
output: html_document
---

# Load Libraries
```{r loadlib, include = F}
library(phyloseq)
library(tidyverse)
library(igraph)
```

# Import data
```{r}
load("outputs/r/2_setup/bh-amp.RData") # bh
load("outputs/r/2_setup/taxo-amp.RData") # taxo.amp
load("outputs/r/2_setup/c100-strat86.RData") # c100_strat86
```

# Flashweave & Cytoscape Prep
```{r}
# Export ASV table
asv.tab <- bh %>%
  merge_samples(group = "genotype", fun = mean) %>% 
  otu_table() %>% 
  as.data.frame()

colnames(asv.tab) <- gsub("ASV ", "ASV",as.character(colnames(asv.tab)))
colnames(asv.tab) <- gsub(": ", "_",as.character(colnames(asv.tab)))

write.csv(asv.tab, 
          file = "data/julia/asv-table-fw.csv",
          quote = F, sep = ",", row.names = F, col.names = T)

# Export tax data
taxo.amp %>% 
  as.data.frame %>% 
  tibble::rownames_to_column("Id") %>% 
  write.csv(file = "data/cytoscape/nodes-taxa.csv", 
              quote = F, sep = ",", row.names = F, col.names = T)


# Get node table from network with sig nodes
nodes <- read.csv(file = "outputs/julia/nodes-hetero-n20-a05-mk3.csv") %>% 
  filter(IsSingleNode != "true") %>%
  select(name, Class, Class_mod, RA, Degree)

# Get assignment table and change names according to node
pv.pb.sp <- c100_strat86 %>%
  select(q_amplicon, type) %>% 
  filter(type == ">99") %>%
  select(q_amplicon)

pv.pb.sp$q_amplicon <- gsub("ASV ", "ASV",as.character(pv.pb.sp$q_amplicon))
pv.pb.sp$q_amplicon <- gsub(": ", "_",as.character(pv.pb.sp$q_amplicon))

# Get RA data and change names according to node
asv <- otu_table(bh)
asv.rel <- apply(vegan::decostand(x = asv, method = "total", MARGIN = 2), 1, mean)
asv.rel <- as.data.frame(asv.rel*100) %>% rownames_to_column()
colnames(asv.rel) <- c("q_amplicon", "RA")

asv.rel$q_amplicon <- gsub("ASV ", "ASV",as.character(asv.rel$q_amplicon))
asv.rel$q_amplicon <- gsub(": ", "_",as.character(asv.rel$q_amplicon))

# Assign RA and recovered taxa
node.rel.rec <- filter(asv.rel, q_amplicon %in% nodes$name) %>%
  mutate(recovered2 = ifelse(q_amplicon %in% pv.pb.sp$q_amplicon, "true", "false")) %>%
  mutate(name2 = q_amplicon)

# Format names to display
node.rel.rec$q_amplicon <- gsub("_", " ",as.character(node.rel.rec$q_amplicon))

node.rel.rec$name2 <- gsub("ASV", "ASV ",as.character(node.rel.rec$name2))
node.rel.rec$name2 <- gsub("_", " ",as.character(node.rel.rec$name2))
node.rel.rec$name2 <- gsub(" sp.", "",as.character(node.rel.rec$name2))
node.rel.rec$name2 <- gsub("Methylobacterium-Methylorubrum", "Methylobacterium",as.character(node.rel.rec$name2))
node.rel.rec$name2 <- gsub("Burkholderia-Caballeronia-Paraburkholderia", "BC-Paraburkholderia",as.character(node.rel.rec$name2))

# write.csv(node.rel.rec, file = "data/cytoscape/nodes-rel-rec.csv",
#           quote = F, sep = ",", row.names = F, col.names = T)

# save(node.rel.rec, file = "outputs/r/Fig_4/nodes-rel-rec.RData")

# Hubs were identified in Cytoscape based on degree, betweeness and closeness centralities thresholds as follows:
# Degree > 7 &
# Betweenness > 0.1 &
# Closeness > 0.3
```

## Plot A: Network
```{r}
# Nw <- grid::rasterGrob(png::readPNG("outputs/r/Fig_4/network-fw-cyt.png"), interpolate = T)

# Add legend
## Node color
df1 <- data.frame(x = factor(1:5), y = rep("Node", 5))
Class <- c("Actinobacteria", "Alphaproteobacteria", "Bacilli", "Bacteroidia", "Gammaproteobacteria")
color.class <- rev(c("#98cc90","#563C5C","#5197c5","#d8cd99","#8A4D30"))

legend1 <- cowplot::get_legend(
  ggplot(df1) +
  geom_point(aes(x = x, y = y, color = x)) +
  scale_color_manual(name = "Class", values = color.class, labels = Class) +
  theme_classic() +
  theme(legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 10),
        legend.key.size = unit(0.5, "cm"),
        legend.key.spacing.x = unit(1, "lines"),
        legend.box.margin = margin(0,0,0,0, "cm"),
        legend.box.spacing = unit(0, "lines"),
        legend.spacing = unit(0, "lines"),
        legend.background = element_rect(fill = "transparent", color = "transparent"))); legend1

## Edge color
df2 <- data.frame(x1 = factor(1:2), x2 = factor(2:3), y1 = factor(1:2), y2 = factor(2:3), color = c("Positive", "Negative"))
Edges <- c("Positive", "Negative")
color.edges <- c("#2abfa4", "#BF592A")

legend2 <- cowplot::get_legend(
  ggplot(df2) +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2 ,color = color)) +
  scale_color_manual(name = "", values = color.edges, labels = Edges) +
  theme_classic() +
  theme(legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 10),
        legend.key.size = unit(0.5, "cm"),
        legend.key.spacing.x = unit(1, "lines"),
        legend.box.margin = margin(0,0,0,0, "cm"),
        legend.box.spacing = unit(0, "lines"),
        legend.spacing = unit(0, "lines"),
        legend.background = element_rect(fill = "transparent", color = "transparent"))); legend2

## Node fill and shape
df3 <- data.frame(x = factor(1:2), y = rep("Hub", 2), color = rep("Cultured", 2))
Cult <- c("Cultured")
legend3 <- cowplot::get_legend(
  ggplot(df3) +
  geom_point(aes(x = x, y = y, shape = y, color = color)) +
  scale_color_manual(name = "", values = c("#BF592A"), labels = Cult) +
  scale_shape_manual(name = "", values = 5) +
  theme_classic() +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 10),
        legend.key.size = unit(0.75, "cm"),
        legend.key.spacing.x = unit(1, "lines"),
        legend.box.margin = margin(0,0,0,0, "cm"),
        legend.box.spacing = unit(0, "lines"),
        legend.spacing = unit(0, "lines"),
        legend.background = element_rect(fill = "transparent", color = "transparent"))); legend3

## Edge size
df4 <- data.frame(x1 = factor(1:3), x2 = factor(4:6), y1 = factor(1:3), y2 = factor(4:6), size = c("0.3", "0.6", "1"))
Size1 <- c(0.35, 0.65, 1.05)

legend4 <- cowplot::get_legend(
  ggplot(df4) +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2 ,size = size)) +
  scale_size_manual(name = "Weight", values = Size1, labels = df4$size) +
  theme_classic() +
  theme(legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 10),
        legend.key.size = unit(0.5, "cm"),
        legend.key.spacing.x = unit(1, "lines"),
        legend.box.margin = margin(0,0,0,0, "cm"),
        legend.box.spacing = unit(0, "lines"),
        legend.spacing = unit(0, "lines"),
        legend.background = element_rect(fill = "transparent", color = "transparent"))); legend4

## Node size
df5 <- data.frame(x = factor(1:6), y = rep("Hub", 6))
Size2 <- c(3, 6, 9, 12, 15, 18)
s.labs <- c("0.001%", "0.01%", "0.1%", "1%", "10%", "20%")
legend5 <- cowplot::get_legend(
  ggplot(df5) +
  geom_point(aes(x = x, y = y, size = x), shape = 21) +
  scale_size_manual(name = "", values = Size2, labels = s.labs) +
  theme_classic() +
  guides(size = guide_legend(title = "Mean rel. ab.", nrow = 1, reverse = F)) +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 10),
        legend.key.size = unit(0.75, "cm"),
        legend.key.spacing.x = unit(1, "lines"),
        legend.box.margin = margin(0,0,0,0, "cm"),
        legend.box.spacing = unit(0, "lines"),
        legend.spacing = unit(0, "lines"),
        legend.background = element_rect(fill = "transparent", color = "transparent"))); legend5

Fig4A <- cowplot::plot_grid(Nw, ncol = 1, labels = c("A"), label_size = 12, vjust = 3, hjust = -18) + 
  theme(plot.margin = margin(0.25, -5, 5, -5, "cm")) +
  annotation_custom(legend1, # Node color
                    xmin = -0.03, xmax = 0.75,
                    ymin = -0.075, ymax = -0.075) +
  annotation_custom(legend2, # Edge color
                    xmin = 0.099, xmax = 0.3,
                    ymin = -0.175, ymax = -0.175) + 
  annotation_custom(legend3, # Node fill and shape
                    xmin = 0.25, xmax = 0.4,
                    ymin = -0.175, ymax = -0.175) + 
  annotation_custom(legend4, # Edge size
                    xmin = 0.35, xmax = 0.6,
                    ymin = -0.175, ymax = -0.175) + 
  annotation_custom(legend5, # Node size
                    xmin = 0, xmax = 0.75,
                    ymin = -0.3, ymax = -0.3)

# save(Fig4A, file = "outputs/r/Fig_4/fig4A.RData")

# cowplot::save_plot(plot = Fig4A,
#   "outputs/r/Fig_4/fig4A.png",
#   base_width = 27,
#   base_height = 18,
#   units = "cm",
#   bg =  "white",
#   scale = 1,
#   dpi = 600)
```

# Network analysis
### Prep
```{r}
load("outputs/r/Fig_4/nodes-rel-rec.RData") # node.rel.rec

nodes <- read.csv(file = "outputs/julia/nodes-hetero-n20-a05-mk3.csv") %>%
  filter(IsSingleNode != "true") %>% mutate(name2 = name) %>% 
  select(-c(Class_mod, IsSingleNode, label, mv, NumberOfDirectedEdges,
            NumberOfUndirectedEdges, PartnerOfMultiEdgedNodePairs, RA, selected, shared.name,
            Species, SelfLoops, name))

nodes$name2 <- gsub("ASV", "ASV ",as.character(nodes$name2))
nodes$name2 <- gsub("_", " ",as.character(nodes$name2))
nodes$name2 <- gsub(" sp.", "",as.character(nodes$name2))
nodes$name2 <- gsub("Methylobacterium-Methylorubrum", "Methylobacterium",as.character(nodes$name2))
nodes$name2 <- gsub("Burkholderia-Caballeronia-Paraburkholderia", "BC-Paraburkholderia",as.character(nodes$name2))

node.data <- merge(nodes, node.rel.rec, by = "name2") %>% 
  select(-c(q_amplicon))

cult <- node.data %>% filter(recovered2 == "true")
  
uncult <- node.data %>% filter(recovered2 == "false")

# To test abundance as a co factor for being peripheral
hra <- node.data %>% filter(RA >= 0.1) # 10/29 uncultured (34%)
lra <- node.data %>% filter(RA < 0.1) # 64/74 uncultured (86)

var <- colnames(node.data); var
```

### Stats
```{r}
# Normality test: p < 0.05 implies sign. differences from the normal dist.
shapiro.test(node.data$RA) # < 2.2e-16
shapiro.test(node.data$Degree) # 1.574e-12 
shapiro.test(node.data$BetweennessCentrality) # 1.599e-14
shapiro.test(node.data$ClosenessCentrality) # < 2.2e-16
shapiro.test(node.data$ClusteringCoefficient) # < 2.2e-16
shapiro.test(node.data$AverageShortestPathLength) # 2.375e-07
shapiro.test(node.data$NeighborhoodConnectivity) # 1.115e-05
shapiro.test(node.data$Stress) # 1.568e-14
shapiro.test(node.data$Eccentricity) # 1.519e-11
shapiro.test(node.data$Radiality) # 2.375e-07
shapiro.test(node.data$TopologicalCoefficient) # 8.947e-08

mwu_RA <- wilcox.test(RA ~ recovered2, node.data); mwu_RA # 1.676e-08 SIG
mwu_D <- wilcox.test(Degree ~ recovered2, node.data); mwu_D # 0.5551 NS
mwu_BC <- wilcox.test(BetweennessCentrality ~ recovered2, node.data); mwu_BC # 0.5064 NS
mwu_CC <- wilcox.test(ClosenessCentrality ~ recovered2, node.data); mwu_CC # 0.007193 SIG
mwu_CCo <- wilcox.test(ClusteringCoefficient ~ recovered2, node.data); mwu_CCo # 0.314 NS
mwu_ASPL <- wilcox.test(AverageShortestPathLength ~ recovered2, node.data); mwu_ASPL # 0.007193 SIG
mwu_NC <- wilcox.test(NeighborhoodConnectivity ~ recovered2, node.data); mwu_NC # 0.003841 SIG
mwu_S <- wilcox.test(Stress ~ recovered2, node.data); mwu_S # 0.4466 NS
mwu_E <- wilcox.test(Eccentricity ~ recovered2, node.data); mwu_E # 0.1314 NS
mwu_R <- wilcox.test(Radiality ~ recovered2, node.data); mwu_R # 0.007193 SIG
mwu_TCo <- wilcox.test(TopologicalCoefficient ~ recovered2, node.data); mwu_TCo # 0.7239 NS
```

#### Closeness Centrality
***Higher values indicate that a node is "close" to others and can easily reach them.***
```{r}
close <- ggplot() +
  geom_density(data = uncult, #hra
               aes(x = ClosenessCentrality, y = stat(count / sum(count)),
               color = recovered2), 
               alpha = 1,
               size = 1) +
  geom_density(data = cult, #lra
               aes(x = ClosenessCentrality, y = stat(count / sum(count)),
               color = recovered2), 
               alpha = 1,
               size = 1) +
  guides(fill = FALSE, color = FALSE) +
  labs(colour = "", x = "Closeness Centrality", y = "Normalized density") +
  theme_classic() +
  scale_x_log10() +
  scale_color_manual(values = c("false" = "#dbdddd", 
                                "true" = "#BF592A")); close
```

#### Average Shortest Path Length
***Lower values imply better network efficiency for information transfer from that node.***
```{r}
aspl <- ggplot() +
  geom_density(data = uncult, 
               aes(x = AverageShortestPathLength, y = stat(count / sum(count)),
               color = recovered2), 
               alpha = 1,
               size = 1) +
  geom_density(data = cult, 
               aes(x = AverageShortestPathLength, y = stat(count / sum(count)),
               color = recovered2), 
               alpha = 1,
               size = 1) +
  guides(fill = FALSE, color = FALSE) +
  labs(colour = "", x = "Average Shortest Path Length", y = "Normalized density") +
  theme_classic() +
  scale_x_log10() +
  scale_color_manual(values = c("false" = "#dbdddd", 
                                "true" = "#BF592A")); aspl
```

#### Neighborhood Connectivity
***Indicates the local connectivity density around a node.***
```{r}
neig <- ggplot() +
  geom_density(data = uncult, 
               aes(x = NeighborhoodConnectivity, y = stat(count / sum(count)),
               color = recovered2), 
               alpha = 1,
               size = 1) +
  geom_density(data = cult, 
               aes(x = NeighborhoodConnectivity, y = stat(count / sum(count)),
               color = recovered2), 
               alpha = 1,
               size = 1) +
  guides(fill = FALSE, color = FALSE) +
  labs(colour = "", x = "Neighborhood Connectivity", y = "Normalized density") +
  theme_classic() +
  scale_x_log10() +
  scale_color_manual(values = c("false" = "#dbdddd", 
                                "true" = "#BF592A")); neig
```

#### Radiality
***Higher values suggest better overall accessibility of a node in the network.***
```{r}
rad <- ggplot() +
  geom_density(data = uncult, 
               aes(x = Radiality, y = stat(count / sum(count)),
               color = recovered2), 
               alpha = 1,
               size = 1) +
  geom_density(data = cult, 
               aes(x = Radiality, y = stat(count / sum(count)),
               color = recovered2), 
               alpha = 1,
               size = 1) +
  guides(fill = FALSE, color = FALSE) +
  labs(colour = "", x = "Radiality", y = "Normalized density") +
  theme_classic() +
  scale_x_log10() +
  scale_color_manual(values = c("false" = "#dbdddd", 
                                "true" = "#BF592A")); rad
```

### Plot B: Distance to Hubs
#### Prep
```{r}
# Load the network
G <- read_graph("outputs/cytoscape/nw_hetero_n20_a05_mk3.gml.graphml", format = "graphml")
G <- as.undirected(G)
print(G)

# Remove nodes with degree 0
G <- delete.vertices(G, which(degree(G) == 0))
# Remove self-loops
G <- simplify(G, remove.multiple = F, remove.loops = T)
print(gorder(G))

# Find hub nodes
hubs <- V(G)[V(G)$Hub == "Yes"]
print(hubs)

# Compute shortest path to the nearest hub
key1 <- "sp_hub_n_hops"
key2 <- "sp_hub_total_weight"
V(G)$sp_hub_n_hops <- Inf
V(G)$sp_hub_total_weight <- Inf
disconnected <- c()

for (source in V(G)) {
  min_hops <- Inf
  min_weight <- Inf
  for (hub in hubs) {
    sp1 <- tryCatch(
      distances(G, v = source, to = hub, weights = NA)[1],
      error = function(e) Inf)
    sp2 <- tryCatch(
      distances(G, v = source, to = hub, weights = E(G)$weight)[1],
      error = function(e) Inf)
    min_hops <- min(min_hops, sp1)
    min_weight <- min(min_weight, sp2)
  }
  V(G)[source]$sp_hub_n_hops <- min_hops
  V(G)[source]$sp_hub_total_weight <- min_weight
  if (min_hops == Inf && min_weight == Inf) {
    disconnected <- c(disconnected, source)
  }
}

# write_graph(G, "outputs/r/Fig_4/sp-hubs.graphml", format = "graphml")

# Separate nodes based on the binary attribute
attribute_key <- "recovered2"
group_0 <- V(G)[!is.na(V(G)$recovered2) & V(G)$recovered2 == F & !(V(G) %in% disconnected)]
group_1 <- V(G)[!is.na(V(G)$recovered2) & V(G)$recovered2 == T & !(V(G) %in% disconnected)]

# Prepare data for plotting
key <- key1 # key2
values0 <- V(G)[group_0]$sp_hub_n_hops
values1 <- V(G)[group_1]$sp_hub_n_hops

data <- data.frame(
  value = c(values0, values1),
  group = c(rep("Uncultured", length(values0)), rep("Cultured", length(values1))))

# Test significance
mwu_hubs <- wilcox.test(value ~ group, data); mwu_hubs # 0.0007538 SIG
```

#### Plot
```{r}
mycolors = c("#BF592A", "#dbdddd")

Fig4B <- ggplot(data,
                aes(x = value,
                   fill = group,
                   color = group)) +
  geom_density(aes(y = ..density..), 
               alpha = 0.75, 
               adjust = 1.5) +
  theme_classic() +
  scale_fill_manual(name = NULL, values = mycolors) +
  scale_color_manual(name = NULL, values = mycolors) +
  labs(y = "Density",
       x = "Shortest-distance to nearest hub") +
  theme(axis.text.x = element_text(size = 8,
                               angle = 0,
                               vjust = 1,
                               hjust = 1),
        axis.text.y = element_text(size = 8,
                               vjust = 0.5,
                               hjust = 1),
        axis.title = element_text(size = 8),
        legend.position = c(0.8, 0.8),
        legend.key.size = unit(0.3, "cm"),
        legend.text = element_text(size = 8),
        legend.title = element_blank(),
        legend.box.margin = margin(0,0,0,0, "cm"),
        legend.background = element_rect(fill = "transparent", color = "transparent"),
        plot.margin = margin(0,0,0,0, "cm")); Fig4B

# save(Fig4B, file = "outputs/r/Fig_4/fig4B.RData")
```

### Plot C: Between group connectivity
#### Prep
```{r}
df.se <- read.csv("outputs/r/Fig_4/shared-edges.csv") %>%
  pivot_longer(cols = c("Cultured", "Uncultured"), names_to = "name", values_to = "value") %>%
  filter(value != 0.5) %>%
  mutate(greater = value > 0.5) %>% #ifelse(value == 0.5, TRUE, value > 0.5)) %>%
  group_by(recovered, name); df.se

tbl.se <- df.se  %>%
  summarise(count = sum(greater), .groups = "keep") %>%
  pivot_wider(names_from = name, values_from = count) %>% 
  column_to_rownames("recovered") ; tbl.se
sum(tbl.se, na.rm = TRUE) # 92/103

# 58 of the uncultured nodes have more than 50% of its edges connected to other uncultured nodes.
# 16 of the uncultured nodes, have more than 50% of its edges connected to cultured nodes.
# 14 of the cultured nodes have more than 50% of its edges connected to other cultured nodes.
# 11 of the cultured nodes have more than 50% of its edges connected to uncultured nodes.

# Test significance
## There is a higher proportion of uncultured nodes that are more connected (>50% edges) to other uncultured nodes than to cultured nodes.
prop.u <- tbl.se %>% rownames_to_column("recovered") %>% filter(recovered == "False") %>% column_to_rownames("recovered")
result <- chisq.test(prop.u) 
print(result) # 2.147e-09 SIG

## There is no difference in the proportion of cultured nodes that are more connected (>50% edges) to other cultured nodes than to uncultured nodes.
prop.c <- tbl.se %>% rownames_to_column("recovered") %>% filter(recovered == "True") %>% column_to_rownames("recovered")
result <- chisq.test(prop.c) 
print(result) # 0.5485 NS
```

#### Plot
```{r}
tbl.se.p <- tbl.se %>% rownames_to_column("Groups") %>% 
  pivot_longer(cols = c("Cultured", "Uncultured"), names_to = "Edges_to", values_to = "value") %>% 
  mutate(Groups = recode(Groups,
                          "False" = "Uncultured",
                          "True" = "Cultured")) %>% 
  mutate(per = round(c(9*100/67, 58*100/67, 14*100/25, 11*100/25),2))

mycolors = c("#BF592A", "#dbdddd")

Fig4C <- ggplot(tbl.se.p) +
  geom_bar(aes(x = Groups, y = per, fill = Edges_to), 
           stat = "identity",
           position = "dodge2") +
  theme_classic() +
  labs(y = "Proportion of ASVs [%]",
       x = "") +
  scale_fill_manual(name = NULL, values = mycolors) +
  scale_color_manual(name = NULL, values = mycolors) +
  theme(axis.text.x = element_text(size = 8,
                               angle = 0,
                               vjust = 0.5,
                               hjust = 0.5),
        axis.text.y = element_text(size = 8,
                               vjust = 0.5,
                               hjust = 0.5),
        axis.title = element_text(size = 8),
        legend.position = "none",
        plot.margin = margin(0,0,0,0, "cm")); Fig4C

# save(Fig4C, file = "outputs/r/Fig_4/fig4C.RData")
```

# Merge final
```{r}
load("outputs/r/Fig_4/fig4A.RData") #Fig4A
load("outputs/r/Fig_4/fig4B.RData") #Fig4B
load("outputs/r/Fig_4/fig4C.RData") #Fig4C

Fig4 <- cowplot::plot_grid(Fig4B, Fig4C,
                           labels = c("B", "C"),
                           label_size = 12,
                           hjust = 1.5,
                           ncol = 1,
                           align = "hv"); Fig4

Fig4_final <- cowplot::plot_grid(Fig4A) +
  annotation_custom(ggplotGrob(Fig4),
                    xmin = 0.725, xmax = 0.975,
                    ymin = 0, ymax = 0.45)

# cowplot::save_plot(plot = Fig4_final,
#   "outputs/r/Fig_4/fig4-final.png",
#   base_width = 27,
#   base_height = 18,
#   units = "cm",
#   bg =  "white",
#   scale = 1,
#   dpi = 600)
```

# SI
```{r}
FigS6 <- cowplot::plot_grid(close, aspl,
                            neig, rad,
                            labels = c("A", "B", "C", "D"),
                            label_size = 12,
                            # vjust = 2,
                            ncol = 2,
                            align = "hv"); FigS6

# cowplot::save_plot(plot = FigS6,
#   "outputs/r/SI/figS6.png",
#   base_width = 27,
#   base_height = 18,
#   units = "cm",
#   bg =  "white",
#   scale = 1,
#   dpi = 600)
```